---
date: "r format(Sys.time(), '%d %B, %Y')"
geometry: margin=2.5cm
linestretch: 2
mainfont: mathptmx
output:
  word_document:
    fig_caption: yes
    fig_width: 7.5
  pdf_document:
    fig_caption: yes
    fig_width: 7.5
    keep_tex: yes
    number_sections: no
  html_document:
    fig_caption: yes
    fig_width: 7.5
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl #Change to desired format
bibliography: references.bib
---
<!-- Install and source necessary packages -->
```{r, echo=FALSE}
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=FALSE)
  library(bibtex)
  
  # List all necessary packages here:
  # install.packages('')
  
  # Source all necessary packages here:
  # library()
```
\pagebreak

# The impact of oil spills on western North American shellfish fisheries {-}

Running Head:

Authors: "Open Science Team"

Institute: $^1$ Department of Biology, University of Victoria, PO BOX 1700 Station CSC, Victoria, British Columbia, V8W 2Y2, Canada $^2$

Corresponding Author:

Keywords: 

\pagebreak

# Abstract {-}

Abstract goes here.


\pagebreak


# Introduction {-}
<!-- Initialize citations -->
```{r, echo=FALSE, include=FALSE}
citep("Article")
# This initializes the citation engine 
```

Make citations like this: [@CITEKEY; @ANOTHERCITEKEY]

## 1. Pollutants and the environment

## 2. Oil spill impacts on ecosystems - toxins, mortality, small-scale vs. notorious (Deepwater, Exxon)

## 3. Oil spill impacts on natural resources - fisheries, lead into inverts

## 4. Examples of oil spill economics/fisheres - stress novelty of examining multiple spills

* Sumaila et al. (2012) used catch estimates to model the effect of the Deepwater oil spill on fisheries value through area closures
* Galicia...
* Exxon-Valdez

# Methods {-}

## Data Sources {-}

We extracted oil spill data from the Emergency Response Division of the National Oceanic and Atmospheric Administration (NOAA; [https://incidentnews.noaa.gov/raw/index](https://incidentnews.noaa.gov/raw/index)) which recorded all major spills that occurred between 1967-2016 in marine environments on the west coasts of U.S.A. and Canada (32.57 - 70.86N&deg;; -179.55 - 116.20W&deg;).   

* Maximum spill size (gallons) was estimated by....  [James waiting on email from NOAA on this]

Fish data were provided by the Sea Around Us Project, which collates global, spatially-explicit estimates of annual fisheries catch at the national level (Pauly & Zeller 2015; Zeller et al. 2016). Taxon-level catch estimates were produced using a combination of international and national catch statistics and, within each exclusive economic zone (EEZ), allocated to 0.5 degree cells using published species distribution data (Pauly & Zeller 2015). From this database, we examined annual commercial fisheries landings data (catch and discards combined, tonnes) for individual species (?) at a 0.5 degree resolution) spanning 1967-2016 for the EEZs of Canada and US (west coast). Data were aggregated according to.....

* Oil and fisheries data were paired by.....



## Data Analysis {-}

**Detrending**
May be a lot of parameters here but there is a lot to control for, potentially might get away with detrending the environmentals or using just an ARMA and include everything we don't care about in an error term or something for everything but discrete events (blooms, oil spills, diseases) which I think should be included explicitly in the model:

N(t+1) = lag*N(t) (autoregressive model) + environmentals (temperature, chl a, pH, El Nino, habitat, prevailing current/wind) + (lags to potential disease outbreaks and algal blooms) + (lag of environmentals) + moving-average model for errors + (lag of oil spills)

**Spill impact analysis**


# Results and discussion {-}

Results and discussion go here

Insert figures like this: 
![Caption](../figures/figurefile.pdf) 

## Caveats (my favourite)

The ecological impact of an oil spill is highly context-dependent, and will be affected by the environmental conditions, clean-up response, and type of oil:

* Environmental conditions: currents, weather, habitat type (?)
* Clean-up response: effectiveness and range in response?
* Type of oil: persistence in environment

The Sea Around Us dataset provided a time-series of spatially-explicit catch data that enabled.....However, such reconstructed catch data are subject to several limitations:

* limitations of SaU?


# Acknowledgements {-}

Travis Tai - mapping code.

# References {-}

```{r, warning=FALSE, message=FALSE, echo=FALSE} 
  write.bibtex(file="references.bib")
```



