---
date: "r format(Sys.time(), '%d %B, %Y')"
geometry: margin=2.5cm
linestretch: 2
mainfont: mathptmx
output:
  word_document:
    fig_caption: yes
    fig_width: 7.5
  pdf_document:
    fig_caption: yes
    fig_width: 7.5
    keep_tex: yes
    number_sections: no
  html_document:
    fig_caption: yes
    fig_width: 7.5
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl #Change to desired format
bibliography: references.bib
---
<!-- Install and source necessary packages -->
```{r, echo=FALSE}
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=FALSE)
  library(bibtex)
  
  # List all necessary packages here:
  # install.packages('')
  
  # Source all necessary packages here:
  # library()
```
\pagebreak

# The impact of oil spills on western North American shellfish fisheries {-}

Running Head:

Authors: "Open Science Team"

Institute: $^1$ Department of Biology, University of Victoria, PO BOX 1700 Station CSC, Victoria, British Columbia, V8W 2Y2, Canada $^2$

Corresponding Author:

Keywords: 

\pagebreak

# Abstract {-}

Abstract goes here.


\pagebreak


# Introduction {-}
<!-- Initialize citations -->
```{r, echo=FALSE, include=FALSE}
citep("Article")
# This initializes the citation engine 
```

Intro goes here.
Make citations like this: [@CITEKEY; @ANOTHERCITEKEY]


# Methods {-}

## Data Sources {-}
Sea Around Us
Oil spill database

## Data Analysis {-}

May be a lot of parameters here but there is a lot to control for, potentially might get away with detrending the environmentals or using just an ARMA and include everything we don't care about in an error term or something for everything but discrete events (blooms, oil spills, diseases) which I think should be included explicitly in the model:

N(t+1) = lag*N(t) (autoregressive model) + environmentals (temperature, chl a, pH, El Nino, habitat, prevailing current/wind) + (lags to potential disease outbreaks and algal blooms) + (lag of environmentals) + moving-average model for errors + (lag of oil spills)



# Results and discussion {-}

Results and discussion go here

Insert figures like this: 
![Caption](../figures/figurefile.pdf) 

# Acknowledgements {-}


# References {-}

```{r, warning=FALSE, message=FALSE, echo=FALSE} 
  write.bibtex(file="references.bib")
```



